### 2017-01-29 manuscript.rmd
added kmrr fib 2a equivalent

@@

		# Merge data of this mrca to the node
		D %<>% left_join(
			nhx@data %>%
				select( D, node, node_age, pic ),
			by = c( "mrca" = "node")

@@

@@

@@

>>>>

		# Add the species
		D %<>% mutate ( species_a = nhx@data$species[ D$tip_a ] )
		D %<>% mutate ( species_b = nhx@data$species[ D$tip_b ] )

@@

		# Merge data of this mrca to the node
		D %<>% left_join(
			nhx@data %>%
				select( D, node, node_age, label, pic ),
			by = c( "mrca" = "node")

@@

	pairwise_summary$Event = NA
	pairwise_summary$Event[ pairwise_summary$D == "N" ] = "Speciation"
	pairwise_summary$Event[ pairwise_summary$D == "Y" ] = "Duplication"

@@

	calibration_times_all = data.frame(
        age =
            c( 20, 92, 167, 9, 42, 74, 296, 535, 104, 937, 29, 722, 441, 65, 15, 1215, 
                414, 371, 162, 25, 74, 77, 86, 7 ), 
        clade = 
            c("Hominoidea", "Euarchontoglires", "Mammalia", "Homininae", 
                    "Simiiformes", "Primates", "Amniota", "Vertebrata", "Eutheria", 
                    "Bilateria", "Catarrhini", "Chordata", "Euteleostomi", 
                    "Haplorrhini", "Hominidae", "Opisthokonta", "Sarcopterygii", 
                    "Tetrapoda", "Theria", "Murinae", "Sciurognathi", "Rodentia", "Glires", "Hominini"
            ),
        stringsAsFactors=FALSE
    )

	pairwise_summary %>% 
		filter( species_a == "homo_sapiens" | species_b == "homo_sapiens" ) %>% 
		filter( ! is.na( D ) ) %>%
		group_by( Event, label ) %>% 
		summarise( cor.test(  tau_a, tau_b )$estimate, n=n() ) %>% 
		rename( rho=`cor.test(tau_a, tau_b)$estimate` ) %>%
		rename( clade = label ) %>% 
		left_join( calibration_times_all, clade=clade ) %>%
		ggplot() + 
			geom_point( aes( x=age, y=rho, col=Event, size=n ) ) +
			theme_classic()

@@

> Figure XX_KMRR_Pairwise | This figures demonstrates that the pairwise analyses presented in Figure 2a of KMRR can be reproduced with the subset of data we consider here and our own independent code base. Each circle indicates the Tau Pearson correlation (rho) for a set of pairwise comparisons annotated with a specific node name of a given age and event type (*i.e.*, whether the divergence at that nodes was due to speciation or duplication). Following KMRR Figure 2a, this figure shows only the comparisons that include a human sequence.
